Visualization of [fulle name] Fractional Integrals

### 2019-05-27 fractional/CMJ style files/article-template.tex
started adding literature review

\documentclass{article}
\usepackage{college-math-j}
\usepackage{xfrac}

@@

%\item[\biogpic{\includegraphics[width=84pt]{Herbert_Hoover.pdf}}Herbert Hoover] (hchoover@stanford.edu) entered Stanford University in 1891, after failing all of the entrance exams except mathematics.  He received his BS degree in geology in 1895, spent time as a mining engineer, then was appointed by his co-author to the U.S. Food Administration and the Supreme Economic Council, where he orchestrated the greatest famine relief efforts of all time.
%\end{biog}
%This is not to say that there  This is partly, because there is no simplistic geometric interpretation for fractional calculus.  
\noindent
Leibniz, who is regarded by many scholars as the farther of calculus, is credited with inventing the following notation: $\frac{d^n y}{d x^n}$. 
A natural question which arises when one inspects this notation is: Can $n$ be a non-integer value? L'Hospital phrased it differently: ``\emph{What if $n$ be a $\frac{1}{2}$?}''. 
In a letter Leibniz sent to L'Hospital, he himself commented on this intriguing question: ``\emph{This is an apparant paradox from which, one day, useful 
consequences will be drawn}.''

The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as fractional calculus. Liouville and Riemann laid most 
of theoretical groundwork which was needed to develop the field of fractional calculus. Fractional calculus has now developed into a mature discipline. 
However, there is one aspect of the discipline which only started to develop fairly recently: its physical and geometric interpretability. At the first international conference on fractional calculus in
New Haven (USA) (which took place in 1974) it was pointed out that literature lacked an acceptable geometric and physical interpretation of fractional calculus. Subsequently, the last few decades has seen 
a number of papers that attempt to rectify this. There now exists probabilistic interpretations, geometric interpretations, physical interpretations and ecenomic 
interpretations of fractional order integrals and differentials.

@@

\begin{thebibliography}{1}
\bibitem{parker13} Adam Parker, Who solved the Bernoulli equation and how did they do it? \textit{Coll. Math. J.} \textbf{44} (2013) 89--97.

>>>>

\documentclass{article}
\usepackage{college-math-j}
\usepackage{xfrac}
\usepackage{textcomp}

@@

%\item[\biogpic{\includegraphics[width=84pt]{Herbert_Hoover.pdf}}Herbert Hoover] (hchoover@stanford.edu) entered Stanford University in 1891, after failing all of the entrance exams except mathematics.  He received his BS degree in geology in 1895, spent time as a mining engineer, then was appointed by his co-author to the U.S. Food Administration and the Supreme Economic Council, where he orchestrated the greatest famine relief efforts of all time.
%\end{biog}
%This is not to say that there  This is partly, because there is no simplistic geometric interpretation for fractional calculus.  
\noindent
Leibniz, who is regarded by many scholars as the farther of calculus, is credited with inventing the following notation: $\frac{d^n y}{d x^n}$. 
A natural question which arises when one inspects this notation is: Can $n$ be a non-integer value? L'Hospital phrased it differently: ``\emph{What if $n$ be a $\frac{1}{2}$?}''. 
In a letter Leibniz sent to L'Hospital, Leibniz comments on L'Hospital's question with the following remark: ``\emph{This is an apparant paradox from which, one day, useful 
consequences will be drawn}'' \cite{ross77,machado14}.\\

\noindent
The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as fractional calculus. Euler, Liouville and Riemann laid most 
of theoretical groundwork which was needed to develop the field of fractional calculus \cite{davis59,liouville1832,riemann1876}. Fractional calculus has now developed into a mature discipline \cite{machado14}. 
However, there is one aspect of the discipline which only started to develop fairly recently: its physical and geometric interpretability. At the first international conference on fractional calculus in
New Haven (USA) (which took place in 1974) it was pointed out that literature lacked an acceptable geometric and physical interpretation of fractional calculus \cite{ross06}. Subsequently, the last few decades has seen 
a number of papers that attempt to rectify this. There now exists probabilistic interpretations, geometric interpretations, physical interpretations and ecenomic 
interpretations of fractional order integrals and differentials.

@@

\begin{thebibliography}{1}

\bibitem{ross77} Ross,~B. (1977). The development of fractional calculus 1695--1900. \textit{Hist. Math.} 4(1): 75--89.

\bibitem{liouville1832} Liouville,~J. (1832). M\'{e}moire sur l\textquotesingle integration de l\textquotesingle \'{e}quation $(mx^2+nx+p)\frac{d^2y}{dx^2}+(qx+r)\frac{dy}{dx}+sy$ \`{a} l\textquotesingle aide des diff\'{e}rentielles \`{a} indices 
que\textquotesingle conques. \textit{Journal d l\textquotesingle Ecole Polytechnique.} 13(21): 163--186.

\bibitem{riemann1876} Riemann,~B.~G.~F (1876). Gesammelte Werke.

\bibitem{davis59} Davis,~P.~J. (1959). "Leonhard Euler's Integral: A Historical Profile of the Gamma Function". \textit{Amer. Math. Monthly}. 66(10): 849--869

\bibitem{machado14} Machado,~J.~T., Galhano,~A.~M., Trujillo,~J.~J. (2014). On development of fractional calculus during the last fifty years. \textit{Scientometrics}. 98(1): 577-582.

\bibitem{ross06} Ross,~B. (Ed.). (2006). \textit{Fractional calculus and its applications: proceedings of the international conference held at the University of New Haven, June 1974}, Vol. 457, Springer.

\bibitem{parker13} Adam Parker, Who solved the Bernoulli equation and how did they do it? \textit{Coll. Math. J.} \textbf{44} (2013) 89--97.
